---
title: "Skill Details"
---
  
  

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(dplyr)
library(kableExtra)
```

```{r functions}
set_spell <- function(name,
                       race,
                       class,
                       background,
                       alignment,
                       notes){
  list("Player" = player_name,
       "Name" = character_name,
       "Race" = race,
       "Class" = class,
       "Background" = background,
       "Alignment" = alignment,
       "Notes" = notes)
}
```

```{r create_tables}

cantrips <- list()

```

**THESE ARE VERRILS SKILLS**

# Cantrips

### Eldritch Blast
**Casting Time:** 1 action    
**Range**: 120 feet    
**Components:** V, S  
**Duration**: Instantaneous  

A beam of crackling energy streaks toward a creature within range. Make a **ranged spell attack** against the target. On a hit, the target takes **1d10 force damage**.  

The spell creates more than one beam when you reach higher levels: two beams at 5th level, three beams at 11th level, and four beams at 17th level. You can direct the beams at the same target or at different ones. Make a separate attack roll for each beam.

### Mage Hand
**Casting Time:** 1 action    
**Range**: 30 feet    
**Components:** V, S  
**Duration**: 1 minute  

A spectral, floating hand appears at a point you choose within range. The hand lasts for the duration or until you dismiss it as an action. The hand vanishes if it is ever more than 30 feet away from you or if you cast this spell again.  

You can use your action to control the hand. You can use the hand to manipulate an object, open an unlocked door or container, stow or retrieve an item from an open container, or pour the contents our of a vial. You can move the hand up to 30 feet each time you use it.  

The hand can't attack, activate magic items, or carry more than 10 pounds.

### Prestidigitation
**Casting Time:** 1 action    
**Range**: 10 feet    
**Components:** V, S  
**Duration**: Up to 1 hour  

This spel is a minor magical trick that novice spellcasters use for practice. You create one of the following magical effects within range.  

+ You create an instantaneous, harmless sensory effect, such as a shower of sparks, a puff of wind, faint musical notes, or an odd odor.
+ You instantaneously light or snuff out a candle, a torch, or a small campfire.
+ You instantaneously clean or soil an object no larger than 1 cubic foot.
+ You chill, warm, or flavor up to 1 cubic foot of nonliving material for 1 hour.
+ You make a color, a small mark, or a symbol appear on an object or a surface for 1 hour.
+ You create a nonmagical trinket or an illusory image that can fit in your hand and that lasts until the end of your next turn.  

If you cast this spell multiple times, you can have up to three of its non-instantaneous effects active at a time, and you can dismiss such an effect as an action.


# Spells
### Burning Hands
**Casting Time:** 1 action    
**Range**: self, (15-foot cone)  
**Components:** V, S  
**Duration**: Instantaneous  

As you hold your hands with thumbs touching and fingers spread, a thin sheet of flames shoots forth from your outstretched fingertips. Each creature in a 15-foot cone must make a Dexterity saving throw. A creature takes **3d6 fire damage** on a failed save, or half as much dammage on a successful one. 

The fire ignotes any flammable object in the area that aren't being worn or carried.  

At higher levels: When you cast this spell using a spell slot of second level or higher, the damage increases by 1d6 for each slot level above 1st.

### Command
**Casting Time:** 1 action    
**Range**: 60 feet  
**Components:** V  
**Duration**: 1 round  

You speak a **one-word command** to a creature you can see within range. The target must succeed on a Wisdom saving throw or follow the command on its next turn. The spell has no effect if the target is undead, if it doesn't understand your language, or if your command is directly harmful to it.  

Some typical commands and their effects follow. You might issue a command other than one described here. If you do so, the DM determines how the target behaves.  
**Approach**. The target moves toward you by the shortest and most direct route, ending its turn if it moves within 5 feet of you.  
**Drop**. The target drops whatever it is holding and then ends its turn.  
**Flee**. The target spends its turn moving away from you by the fastest avaialble means.  
**Grovel**. When you case this spell using a spell slot of 2nd level or higher, you can affect one addtitional creature for each slot level above 1st. The creature must be within 30 feet of each other when you target them.

### Hex
**Casting Time:** 1 bonus action  
**Range**: 90 feet  
**Components:** V, S, M (the petrified eye of a newt)   
**Duration**: Concentration, up to 1 hour    

You place a curse on a creature that you can see within range. Until the spell ends, you deal an extra **1d6 necrotic damage** to the target whenever you hit it with an attack. Also, **choose one ability** when you case the spell. The target has disadvantage on ability checks made with the chosen ability.  

If the target drops to 0 hit points before this spell ends, you can use a bonus action on a subsequent turn of yours to curse a new creature.  
A *remove curse* cast on the target ends this spell early.  

At Higher Levels. When you cast this spell using a spell slot of 3rd or 4th level, you can maintain your concentration on the spell for up to 8 hours. When you use a spell slot of 5th level or higher, you can maintain your concentration on the spell for up to 24 hours.

# Eldritch Invocations

### Agonizing Blast
When you cast *eldritch blast*, add your Charisma modifier to the damage it deals on a hit.


### Devil's Sight
You can see normally in darkness, both magical and nonmagical, to a distance of 120 feet.


### Fiendish Vigor
You can cast *false life* on yourself at will as a 1st-level spell, without expending a spel slot or material components.  

**False life**   
<div style="font-size: 0.8em;padding-left:30px">
**Casting Time**: 1 action  
**Range**: Self  
**Components**: V, S, M (a small amount of alcohol or distilled spirits)  
**Duration**: 1 hour    

Bolstering yourself with a necromantic facsimile of life, you gain **1d4 + 4 temporary hit points** for the duration.    

At Higher Levels. When you cast this spell using a spell slot of 2nd level or higher, you gain 5 additional temporary hit points for each slot level above 1st.
</div>


### Mask of Many Faces
You can cast *disguise self* at will, without expending a spell slot.

**Disguise self**
<div style="font-size: 0.8em;padding-left:30px">
**Casting Time**: 1 action  
**Range**: Self  
**Components**: V, S 
**Duration**: 1 hour    

You make yourself -- including your clothing, armour, weapons, and other belongings on your person -- look different until the spell ends or until you use your action to dismiss it. You can seem 1 foot shorter or taller and can appear thin, fat, or in between. You can't change your body type, so you must adopt a form that has the same basic arrangement of limbs. Otherwise, the extent of the illusion is up to you.  

The changes wrought by this spell fail to hold up to physical inspection. For example, if you use this spell to add a hat to your outfit, objects pass through the hat, and anyone who touches it would feel nothing or would feel your head and hair. If you use this spell to appear thinner than you are, the hand of someone who reaches out to touch you would bump into you while it seemingly still in midair.  

To discern that you are disguised, a creature can use its action to inspect your appearance and must succeed on an Intelligence (Investigation) check against your spell save DC.
</div>
